What if you drop that? Modeling children's curiosity about physical interactions

### 2020-02-04 paper/paper.Rmd
better graphs

length(unique(tower$SID)) #61
length(unique(hum$SID)) # 51 subjects

@@

First we examine tower height as a function of age, finding that older children tend to build higher towers `r cor_apa(ht_age, format="rmarkdown", print=F)`.

```{r plot-height-by-age, include=F}
ch_height <- hum %>% group_by(age_rounded, height_tallest) %>%
  summarise(n = n()) %>%
  mutate(freq = n / sum(n))

@@

2. support x supported (counts)
```{r heatmap-support-by-supported-counts}
tower = subset(tower, tallest_objects!="" & tallest_objects!="pentagon+octahedron, trig prism") # 5 kids who arranged horizontally and 1 kid chose 2 - exclude
df = data.frame(support=NA, supported=NA, n=NA)
for(s in 1:nrow(tower)) {
  objs = unlist(str_split(tower[s,]$tallest_objects, ", "))
  print(objs)
  for(i in 2:length(objs)) {
    df = rbind(df, cbind(support=objs[i-1], supported=objs[i], n=1))
  }
}
df = na.omit(df)
hm <- df %>% group_by(support, supported) %>% count(N=n()) 
hm %>% ggplot(aes(x=support, y=supported)) + geom_tile(aes(fill=N)) + geom_text(aes(label = N)) +
  scale_fill_gradient(low = "white", high = "steelblue") + ggthemes::theme_few()
```

3. support x supported (probabilities)
pr (supported object | support object)
```{r heatmap-support-by-supported-probs}
tower = subset(tower, tallest_objects!="" & tallest_objects!="pentagon+octahedron, trig prism") # 5 kids who arranged horizontally and 1 kid chose 2 - exclude
df = data.frame(support=NA, supported=NA, n=NA)
for(s in 1:nrow(tower)) {
  objs = unlist(str_split(tower[s,]$tallest_objects, ", "))
  print(objs)
  for(i in 2:length(objs)) {
    df = rbind(df, cbind(support=objs[i-1], supported=objs[i], n=1))
  }
}
df = na.omit(df)
hm1 <- df %>% 
  group_by(support, supported) %>% 
  summarise(n = n()) %>% 
  group_by(support) %>%
  mutate(freq = n / sum(n))
hm1 %>% ggplot(aes(x=support, y=supported)) + geom_tile(aes(fill=freq)) + geom_text(aes(label = round(freq, 2))) +
  scale_fill_gradient(low = "white", high = "steelblue") + ggthemes::theme_few()
```

4. base and top distribution
```{r base-and-top-objects}
ch_extremes <- hum %>% 
  group_by(base_tallest) %>% 
  count(N=n()) %>%
  filter(base_tallest!="" & base_tallest!="pentagon+octahedron")

@@

<!-- 1. height x age -->
<!-- -First we examine tower height, of the tallest stack, as a function of age. We find tower height increases with age (cor.test). -->

@@

rand_drop <- drop_choice_plot(subset(md, policy=="random"), Shapes)
curio_drop <- drop_choice_plot(subset(md, policy=="curious"), Shapes)
noncurio_drop <- drop_choice_plot(subset(md, policy=="noncurious"), Shapes)

@@

```{r combined-model-fig, fig.env = "figure*", fig.pos = "h", fig.align="center", fig.width=7, fig.height=3.2, set.cap.width=T, num.cols.cap=2, fig.cap = "Relative frequency of objects chosen by each model as objects for dropping (first row), and objects hit as targets (second row; pink dots represent hitting empty space), as a function of target/drop set pairing."}

ggarrange(rand_drop, curio_drop, noncurio_drop, 
          rand_targ, curio_targ, noncurio_targ, ncol=3, nrow=2, 
          labels = c("Random", "Curious", "Noncurious"),
          common.legend=T, legend="bottom")
```

>>>>

#length(unique(tower$SID)) #61
Nsubj_tower = length(unique(hum$SID)) # 51 subjects

@@

The average height of the constructed towers was `r round(mean(na.omit(hum$height_tallest)), 1)` blocks.
We examined tower height as a function of age, and found that older children tend to build higher towers (`r cor_apa(ht_age, format="rmarkdown", print=F)`).

```{r plot-height-by-age, include=F, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Tower height by age."}
ch_height <- hum %>% group_by(age_rounded, height_tallest) %>%
  summarise(n = n()) %>%
  mutate(freq = n / sum(n))

@@

Next we examine the number of times participants supported each object with each other object. 
```{r heatmap-support-by-supported-counts, include=T, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Counts of support and supported object relations in participants' towers."}
tower = subset(tower, tallest_objects!="" & tallest_objects!="pentagon+octahedron, trig prism") # 5 kids who arranged horizontally and 1 kid chose 2 - exclude
df = data.frame(support=NA, supported=NA, n=NA)
for(s in 1:nrow(tower)) {
  objs = unlist(str_split(tower[s,]$tallest_objects, ", "))
  #print(objs)
  for(i in 2:length(objs)) {
    df = rbind(df, cbind(support=objs[i-1], supported=objs[i], n=1))
  }
}
df = na.omit(df)
hm <- df %>% group_by(support, supported) %>% count(N=n()) 
hm %>% ggplot(aes(x=support, y=supported)) + geom_tile(aes(fill=N)) + geom_text(aes(label = N)) +
  scale_fill_gradient(low = "white", high = "steelblue") + ggthemes::theme_few()
```

(Could instead show P(supported object | support object).)
```{r heatmap-support-by-supported-probs, include=F, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Conditional probabilities of supported object given support object in participants' towers."}
tower = subset(tower, tallest_objects!="" & tallest_objects!="pentagon+octahedron, trig prism") # 5 kids who arranged horizontally and 1 kid chose 2 - exclude
df = data.frame(support=NA, supported=NA, n=NA)
for(s in 1:nrow(tower)) {
  objs = unlist(str_split(tower[s,]$tallest_objects, ", "))
  print(objs)
  for(i in 2:length(objs)) {
    df = rbind(df, cbind(support=objs[i-1], supported=objs[i], n=1))
  }
}
df = na.omit(df)
hm1 <- df %>% 
  group_by(support, supported) %>% 
  summarise(n = n()) %>% 
  group_by(support) %>%
  mutate(freq = n / sum(n))
hm1 %>% ggplot(aes(x=support, y=supported)) + geom_tile(aes(fill=freq)) + geom_text(aes(label = round(freq, 2))) +
  scale_fill_gradient(low = "white", high = "steelblue") + ggthemes::theme_few()
```

<!-- Finally, we look at the distribution of tower heights as a function of the objects chosen as the base of the tower. -->

```{r base-and-top-objects, include=F, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.cap = "Distribution of base and top objects in participants' towers."}
ch_extremes <- hum %>% 
  group_by(base_tallest) %>% 
  count(N=n()) %>%
  filter(base_tallest!="" & base_tallest!="pentagon+octahedron")

@@

@@

rand_drop <- drop_choice_plot(subset(md, policy=="random"), ymax=1, Shapes) + ggtitle("Random")
curio_drop <- drop_choice_plot(subset(md, policy=="curious"), ymax=1, Shapes) + ggtitle("Curious")
noncurio_drop <- drop_choice_plot(subset(md, policy=="noncurious"), ymax=1, Shapes) + ggtitle("Noncurious")

@@

```{r combined-model-fig, fig.env = "figure*", fig.pos = "h", fig.align="center", fig.width=7, fig.height=5.5, set.cap.width=T, num.cols.cap=2, fig.cap = "Relative frequency of objects chosen by each model as objects for dropping (first row), and objects hit as targets (second row; pink dots represent hitting empty space), as a function of target/drop set pairing."}

ggarrange(rand_drop, curio_drop, noncurio_drop, 
          rand_targ, curio_targ, noncurio_targ, ncol=3, nrow=2, #labels = c("A", "B", "C"),
          common.legend=T, legend="bottom")
```
